full title

### 2020-11-20 paper/pldi21/intro.tex
Till Sec. 2

\section{Introduction}\label{sec:intro}
Over the past decades, the rise of JavaScript as the de facto programming
language for web development has expanded its reach to diverse fields.
Node.js~\cite{nodejs} supports server-side programming, React
Native~\cite{react-native} and Electron~\cite{electron} produce cross-platform
applications, and Moddable~\cite{moddable} and Espruino~\cite{espruino}
provide JavaScript environments in micro-controllers for IoT.  Such wide prevalent
uses place JavaScript at \#7 in the TIOBE Programming Community
index\footnote{https://www.tiobe.com/tiobe-index/}.  Thus, researchers have
developed static analyzers such as JSAI~\cite{jsai}, TAJS~\cite{tajs},
WALA~\cite{wala}, and SAFE~\cite{safe,safe2} to understand behaviors of
JavaScript programs and to detect their bugs in a sound manner.

@@

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis by taking
multiple dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of existing analyzers SAFE and Jalangi.
\item For empirical evaluation, we analyzed \inred{77} official tests of
\inred{Lodash 4} library.  The experiment shows that $\tool$ outperforms
SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{XX.X} opaque functions,
$\tool$ improves \inred{XX.XX}\% of the analysis precision on average.
\end{itemize}

>>>>

\section{Introduction}\label{sec:intro}
Over the past decades, the rise of JavaScript as the de facto
language for web development has expanded its reach to diverse fields.
Node.js~\cite{nodejs} supports server-side programming, React
Native~\cite{react-native} and Electron~\cite{electron} produce cross-platform
applications, and Moddable~\cite{moddable} and Espruino~\cite{espruino}
provide JavaScript environments in micro-controllers for IoT.  Such wide prevalent
uses place JavaScript at \#7 in the TIOBE Programming Community
index\footnote{https://www.tiobe.com/tiobe-index/}.  Thus, researchers have
developed static analyzers such as JSAI~\cite{jsai}, TAJS~\cite{tajs},
WALA~\cite{wala}, and SAFE~\cite{safe,safe2} to understand behaviors of
JavaScript programs and to detect their bugs in a sound manner.

@@

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis using
dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of SAFE and Jalangi.
\item For empirical evaluation, we analyzed \inred{77} official tests of
\inred{Lodash 4} library.  The experiment shows that $\tool$ outperforms
SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{XX.X} opaque functions,
$\tool$ improves \inred{XX.XX}\% of the analysis precision on average.
\end{itemize}

### 2020-11-20 paper/pldi21/motivation.tex
Till Sec. 2

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var array = arguments[0],
      args  = Array(length - 1),
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(isArray(array) ?
    copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function.}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) {
  ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load the list of states of the United States.}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option of server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load more Zoom events from the server.}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
  in \code{zoom.us} site.}
  \label{fig:example}
  \vspace*{-1em}
\end{figure}

In this section, we will explain the motivation of the dynamic shortcut for
JavaScript static analysis with real-world examples described in
Figure~\ref{fig:example}.  We first describe their program behaviors and then
explain how to utilize dynamic analysis during static analysis of them.

For motivating examples, we excerpt the \jscode{concat} function in
Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
function creates a new array concatenating given arrays or values.  It first
checks the length of arguments in line 1-3. Then, it stores the first argument
to \jscode{array} in line 4 and copies the remaining arguments to \jscode{args} in
line 5-8.  In line 9, it checks whether \jscode{array} is an array object with
the built-in function \jscode{isArray}.  If so, it creates a new array by
copying the given array via or initializing with a single value in line 10.
Finally, it flattens \jscode{args} via \jscode{baseFlatten} and pushes the
result to the new array in line 11.

For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
homepage of Zoom, which is a videotelephony software program developed by Zooom
Video Communications and it is ranked as \inred{16th} popular web site according
to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

\paragraph{Dynamic shortcut with concrete values.}
When the given arguments of a function are concrete values, we can perform
dynamic analysis instead of static analysis. For example, the
\jscode{changeCountry} function is invoked when a user selects another country
on the drop-down list in the registration page.  It calls the \jscode{concat}
function to update the drop-down list of states or provinces in 17-18.  However,
when the user selects ``United States of America'' (USA), two arguments are
pre-defined with deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs of
abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
\jscode{concat} function with \jscode{\_} as \jscode{this} value and above two
concrete values as arguments.  It increases performance of static analysis by
skipping the analysis of function call in line 17-18 and utilizing the result of
dynamic analysis.

\begin{figure}[t]
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \top & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \symb_\jscode{int}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{this.pastEvents}}
    \label{fig:pastEvents}
  \end{subfigure}
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \jscode{0} & \symb_\jscode{evt}\\\hline
        \cdots & \cdots\\\hline
        \jscode{7} & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \jscode{8}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{e.events}}
    \label{fig:events}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Concrete objects for arguments with sealed symbolic values.}
  \label{fig:sealed}
  \vspace*{-1em}
\end{figure}

\paragraph{Dynamic shortcut with abstract values.}
Dynamic analysis is still applicable using \textit{sealed symbolic execution}
even if the arguments are not concrete values.  The \jscode{getData} function is
invoked when clicking the ``Load More'' button to load more Zoom events in
``Webinars \& Events'' page.  For each click, the \jscode{getData} sends a POST
request to the server and receives additional event information \jscode{e} in
line 24.  Then, eight events in \jscode{e.events} are appended to
\jscode{this.pastEvents} using the \jscode{concat} function in line 27-28.
However, the arguments of \jscode{concat} are not deterministic because 1) the
event list stored in \jscode{this.pastEvents} is continuously grown for each
load and 2) also each event stored in \jscode{e.events} are dependent on the
data given from the server.

To perform dynamic analysis with abstract values, we sealed the abstract values
of arguments with symbolic values as described in Figure~\ref{fig:sealed}.  It
contains two symbolic values $\symbevt$ and $\symbint$ that represent any event
objects and integer values, respectively.  Then, dynamic analysis is
successfully performed before copying \jscode{array} via \jscode{copyArray} in
line 10.  First, \jscode{length} stores \jscode{2} and passes the length check
in line 1-2. Then, \jscode{array} points to the same object of
\jscode{this.pastEvents} in line 4, \jscode{args} stores an array with a
single object stored in \jscode{e.events} in 5-8, and the \jscode{isArray}
function returns \jscode{true} for \jscode{array} in line 9.  However, it fails
to perform dynamic analysis for \jscode{copyArray} because the \jscode{length}
property of \jscode{array} is the symbolic value $\symbint$.  Thus, the dynamic
shortcut returns the analysis result and the static analyzer continues to
analyze the program from line 10.  Then, only copying via \jscode{copyArray},
flattening via \jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize
the abstract semantics.  This is how to utilize sealed symbolic execution to
maximize the part of dynamic analysis during static analysis.

\paragraph{Dynamic shortcut for opaque functions.}

The previous two examples also show that dynamic shortcut can improve the
analysis precision and lessen the effort of modeling the opaque functions.
In line 9, the \jscode{isArray} function is a JavaScript built-in library thus
it is written in a native language of the host environment.  Thus, we need to
manually model its behavior to statically analyze it.  Assume that we model the
\jscode{isArray} function to return the top boolean value that denotes both of
\jscode{true} and \jscode{false}.  If we perform static analysis with this
modeling, both of true branch \jscode{copyArray(array)} and false branch
\jscode{[array]} in line 10 are always analyzed while \jscode{[array]} is never
reachable in the motivating examples.  However, with the dynamic shortcut, the
analyzer utilizes the concrete semantics of \jscode{isArray}.  It returns more
precise result \jscode{true} instead of the top boolean value and it is not
necessary to model the \jscode{isArray} function for static analysis of
motivating examples.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var array = arguments[0],
      args  = Array(length - 1),
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(isArray(array) ?
    copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) { ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Call of \jscode{concat} with concrete values}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option for server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Call of \jscode{concat} with abstract values}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Lodash library function and its uses in \code{zoom.us}}
  \label{fig:example}
  \vspace*{-1em}
\end{figure}

In this section, we explain the motivation of dynamic shortcuts
using real-world examples shown in Figure~\ref{fig:example}.
We first describe their behaviors and then explain how we can utilize
dynamic shortcuts during their static analysis.

Figure~\ref{fig:example}(a) shows the \jscode{concat} function defined
in Lodash library~\cite{lodash} (v4.17.20); it is
the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
and \inred{124,562} npm packages have a dependency on it.
The \jscode{concat} function creates a new array concatenating given arrays or values.
It first checks the length of \jscode{arguments} on lines 1--3.
Then, it stores the first argument to \jscode{array} on line 4 and
copies the remaining arguments to \jscode{args} on lines 5--8.
On line 9, it checks whether \jscode{array} is an array object using
the built-in function \jscode{isArray}.  If so, it creates a new array
by copying the given array via \jscode{copyArray}; otherwise,
it creates a singleton array \jscode{[array]}.  Finally, it flattens
\jscode{args} via \jscode{baseFlatten} and pushes the result to the
new array on line 11.

Figure~\ref{fig:example}(b) and Figure~\ref{fig:example}(c) show use
cases of the \jscode{concat} function in the \code{zoom.us}~\cite{zoom} site.
It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
Video Communications and it is ranked as the \inred{16th} popular web site according
to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

\paragraph{Dynamic shortcuts with concrete values.}
When a function is called with concrete values, we can perform
dynamic analysis instead of static analysis.
For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
is invoked when a user selects a country from a drop-down list in the registration page.
It calls the \jscode{concat} function to update the drop-down list of
states or provinces on lines 17--18.  However, when the user selects ``United States of America,''
which is \jscode{"US"}, two arguments are pre-defined with
deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs
of abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
Thus, we can perform dynamic analysis by invoking \jscode{concat} with
\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
By skipping the analysis of the function call on lines 17--18 and
utilizing the result of dynamic analysis, it improved the analysis performance.

\begin{figure}[t]
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \top & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \symb_\jscode{int}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{this.pastEvents}}
    \label{fig:pastEvents}
  \end{subfigure}
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \jscode{0} & \symb_\jscode{evt}\\\hline
        \cdots & \cdots\\\hline
        \jscode{7} & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \jscode{8}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{e.events}}
    \label{fig:events}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Concrete objects with sealed symbolic values}
  \label{fig:sealed}
  \vspace*{-1em}
\end{figure}

\paragraph{Dynamic shortcuts with abstract values.}
Even when a function is called with abstract values, we can still
perform dynamic analysis using sealed symbolic execution.
For example, \jscode{getData} in Figure~\ref{fig:example}(c) is invoked
when a user clicks the ``Load More'' button to load more Zoom events in
the ``Webinars \& Events'' page.  It sends a POST
request to a server and receives additional events \jscode{e} on
line 24.  Then, eight events in \jscode{e.events} are appended to
\jscode{this.pastEvents} using \jscode{concat} on lines 27--28.
However, the arguments of \jscode{concat} are not deterministic because 1) the
event list stored in \jscode{this.pastEvents} is continuously grown for each
load and 2) the events stored in \jscode{e.events} are dependent on the
data given from the server.

To perform dynamic analysis with abstract values, we seal abstract values
with symbolic values as in Figure~\ref{fig:sealed}.  Two symbolic
values $\symbevt$ and $\symbint$ represent an event
object and an integer, respectively.  Then, we can perform dynamic analysis
successfully until line 9.  On line 2, \jscode{length} is \jscode{2};
on line 4, \jscode{array} points to \jscode{this.pastEvents};
on lines 5--8, \jscode{args} stores an array with a single object stored in \jscode{e.events};
and on line 9, \jscode{isArray(array)} is \jscode{true}.
However, dynamic analysis fails for \jscode{copyArray(array)} on line 10
because the value of the \jscode{length} property of \jscode{array} is the symbolic value $\symbint$.
Then, we stop the sealed symbolic execution, convert the current
sealed symbolic state to its corresponding abstract state, and resume
the static analysis from line 10.  Because sealed symbolic execution
leverages fast dynamic analysis as long as possible, the overall
analysis becomes more scalable.

\paragraph{Dynamic shortcuts for opaque functions.}
As the previous two examples additionally show, using dynamic shortcuts 
lessens the burden of modeling opaque functions from static analysis, and
it can even improve the analysis precision.
On line 9, since the \jscode{isArray} function is a JavaScript built-in library function,
it is implemented in a native language of the host environment, which
often requires manual modeling of its behaviors for JavaScript static analysis.
Assuming that a static analyzer models \jscode{isArray} to return the
boolean top value $\top_b$ that encompasses both \jscode{true} and \jscode{false},
static analysis of the ternary conditional expression on lines 9--10 analyzes
both branches \jscode{copyArray(array)} and \jscode{[array]}, even though
\jscode{[array]} is never reachable in the example code.  On the contrary,
using dynamic shortcuts, static analysis does not need to model \jscode{isArray}.
It can perform sealed symbolic execution for \jscode{isArray}, which
returns a more precise result \jscode{true} than $\top_b$.
